Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion

### 2018-09-21 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Minor fixes to the topic models

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "Government policy is partly driven by the topics that are discussed in parliament. Conversely, those same topics can indicate a government's priorities. But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary debate. In this paper, we systematically analyse how parliamentary debate has changed in response to different types of events in Australian history. We compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. We use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time. We then examine the effect of various events using a discrete choice model. We find that: 1) changes of government are associated with topic changes only when there is also a change of the party in power; and 2) economic events, such as financial crises, have significant and persistent effects. Our findings have implications for how we think about the longer-term trajectory of government policy as the media cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different to the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal predecessor Kevin Rudd's carbon tax. Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government. However it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.

@@

Australian Hansard records have been analysed for various purposes, but usually not at larger-scale. For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. And @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.

Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release. There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**. As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in the Appendix.

@@

The main sources for this additional supplementary information are the handbooks supplied by the various parliaments (Table 2).

| Parliament  | House  | Source |
|:------|-----:|---------:|
| Commonwealth      | House of Representatives | Parliamentary Handbok |
|                   | Senate                   | **[TBD]** |
| Queensland        | Legislative Assembly     |  **[TBD]** |
|                   | Legislative Council      | **[TBD]** |
| New South Wales   | Legislative Assembly     | **[TBD]** |
|                   | Legislative Council      | **[TBD]** |
| Victoria          | Legislative Assembly     | **[TBD]** |
|                   | Legislative Council      | **[TBD]** |
| Tasmania          | House of Assembly        | **[TBD]** |
|                   | Legislative Council      |  **[TBD]** |
| South Australia   | House of Assembly        | **[TBD]** |
|                   | Legislative Council      | **[TBD]** |
| Western Australia | Legislative Assembly     | **[TBD]** |
|                   | Legislative Council      | **[TBD]** |

The additional information from the handbooks had many errors and it was supplemented by data from the Australian Dictionary of Biography and Wikipedia.[^seeMyAdditionalData]

@@

# Model
The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage. The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent. In this section a brief overview of both the LDA model and the STM approach is provided. In a similar way to @MuellerRauh2018 we consider the outputs of the topic model as reduced dimension inputs. In our case they are inputs to a discrete choice model, and so we then discuss that model.

>>>>

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard and Matthew Kerby for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "Government policy is partly driven by the topics that are discussed in parliament. Conversely, those same topics can indicate a government's priorities. But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary debate. In this paper, we systematically analyse how parliamentary debate has changed in response to different types of events in Australian history. We compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. We use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time. We then examine the effect of various events using a discrete choice model. We find that: 1) changes of government are associated with topic changes only when there is also a change of the party in power; and 2) economic events, such as financial crises, have significant and persistent effects. Our findings have implications for how we think about the longer-term trajectory of government policy as the media cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different to the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal his predecessor Kevin Rudd's carbon tax. Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government. However it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.

@@

Australian Hansard records have been analysed for various purposes, but usually at a more-specific level than we do here. For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. And @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.

Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release. There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records publicly available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**. As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in the Appendix.

@@

The main sources for this additional supplementary information are the handbooks supplied by the various parliaments. However these had many errors and were supplemented by data from the Australian Dictionary of Biography and Wikipedia.[^seeMyAdditionalData]

@@

# Model
The main models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**. Theoretically we could have directly used the text as an input to the discrete choice model, but this is intractable due to computer memory and storage constraints. Instead, in a similar way to @MuellerRauh2018, we use the topics that the text is about as an input to another model, which in our case is a discrete choice model.

The basis of the STM is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent. In this section we provide a brief overview of both the LDA model and the STM.  we consider the outputs of the topic model as reduced dimension inputs. In our case they are inputs to a discrete choice model, and so we then discuss that model.

### 2018-09-21 outputs/docs/events/svm-rmarkdown-article-example.tex
Minor fixes to the topic models

\title{Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
suggestions. \textbf{Version as of}: September 18, 2018;
\textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

New governments often go to some trouble to be different to the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was not supported by his predecessor John Howard,
and then one of Tony Abbott's first acts was to repeal predecessor Kevin
Rudd's carbon tax. Similarly, significant events such as the 9/11
attacks or the Great Recession have often altered the course of a
government. However it is not so clear which events drive changes, for
how long these changes persist, and what was given up due to the change.

@@

Australian Hansard records have been analysed for various purposes, but
usually not at larger-scale. For instance, \citet{Rasiah2010} examined
Hansard records for the Australian House of Representatives to examine
whether politicians attempted to evade questions about Iraq during
February and March 2003. And \citet{GansLeigh2012} examined Australian
Hansard records to associate mentions by politicians of certain public
intellectuals with neutral or positive sentiment.

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
There is a more limited set of XML records available in some
cases.\footnote{Tim Sherratt makes these XML records available as a
  single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through today from Open Australia's website.} There are
65,000 \textbf{{[}UPDATE{]}} Hansard records available across the state
and federal parliaments (Table 1) \textbf{{[}UPDATE NUMBERING{]}}. As
with any larger-scale data process, there are various issues with some
of the PDFs and the known ones are detailed in the Appendix.

@@

The main sources for this additional supplementary information are the
handbooks supplied by the various parliaments (Table 2).

\begin{longtable}[]{@{}lrr@{}}
\toprule
Parliament & House & Source\tabularnewline
\midrule
\endhead
Commonwealth & House of Representatives & Parliamentary
Handbok\tabularnewline
& Senate & \textbf{{[}TBD{]}}\tabularnewline
Queensland & Legislative Assembly & \textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
New South Wales & Legislative Assembly &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
Victoria & Legislative Assembly & \textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
Tasmania & House of Assembly & \textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
South Australia & House of Assembly & \textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
Western Australia & Legislative Assembly &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
\bottomrule
\end{longtable}

The additional information from the handbooks had many errors and it was
supplemented by data from the Australian Dictionary of Biography and
Wikipedia.\footnote{An example of the additional information is provided
  in the Appendix. The datasets are available on request.}

@@

The main model that we use in this paper is the Structural Topic Model
(STM) as implemented by the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}. The basis of this type of topic
modelling is the Latent Dirichlet Allocation (LDA) model of
\citet{Blei2003latent}. In this section a brief overview of both the LDA
model and the STM approach is provided. In a similar way to
\citet{MuellerRauh2018} we consider the outputs of the topic model as
reduced dimension inputs. In our case they are inputs to a discrete
choice model, and so we then discuss that model.

>>>>

\title{Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
suggestions. \textbf{Version as of}: September 20, 2018;
\textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

New governments often go to some trouble to be different to the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was not supported by his predecessor John Howard,
and then one of Tony Abbott's first acts was to repeal his predecessor
Kevin Rudd's carbon tax. Similarly, significant events such as the 9/11
attacks or the Great Recession have often altered the course of a
government. However it is not so clear which events drive changes, for
how long these changes persist, and what was given up due to the change.

@@

Australian Hansard records have been analysed for various purposes, but
usually at a more-specific level than we do here. For instance,
\citet{Rasiah2010} examined Hansard records for the Australian House of
Representatives to examine whether politicians attempted to evade
questions about Iraq during February and March 2003. And
\citet{GansLeigh2012} examined Australian Hansard records to associate
mentions by politicians of certain public intellectuals with neutral or
positive sentiment.

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
There is a more limited set of XML records available in some
cases.\footnote{Tim Sherratt makes these XML records available as a
  single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through today from Open Australia's website.} There are
65,000 \textbf{{[}UPDATE{]}} Hansard records publicly available across
the state and federal parliaments (Table 1) \textbf{{[}UPDATE
NUMBERING{]}}. As with any larger-scale data process, there are various
issues with some of the PDFs and the known ones are detailed in the
Appendix.

@@

The main sources for this additional supplementary information are the
handbooks supplied by the various parliaments. However these had many
errors and were supplemented by data from the Australian Dictionary of
Biography and Wikipedia.\footnote{An example of the additional
  information is provided in the Appendix. The datasets are available on
  request.}

@@

The main models that we use in this paper are the Structural Topic Model
(STM) as implemented by the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}, and a discrete choice model as
implemented by the \texttt{XXXX} R package of \textbf{XYZ}.
Theoretically we could have directly used the text as an input to the
discrete choice model, but this is intractable due to computer memory
and storage constraints. Instead, in a similar way to
\citet{MuellerRauh2018}, we use the topics that the text is about as an
input to another model, which in our case is a discrete choice model.

The basis of the STM is the Latent Dirichlet Allocation (LDA) model of
\citet{Blei2003latent}. In this section we provide a brief overview of
both the LDA model and the STM. we consider the outputs of the topic
model as reduced dimension inputs. In our case they are inputs to a
discrete choice model, and so we then discuss that model.
